---
title: "Sillence_InteractionPowerR"
author: "Ethan C. Brown"
date: "2022-12-12"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(InteractionPoweR)
library(tidyverse)
library(pwr2ppl)

```

Replicate analysis from correlations alone
```{r replicate_corr}

## y = SFU
## x1 = FA
## x2 = SA
MRC_shortcuts(ry1=-.18,
    ry2=-.03,
    ry3=-0.02, 
    r12=.64,
    ## Drawn from supplemental materials
    ## Unfortunately, these correlations would be drawn from summed (not centered) variables
    ## Correlations may differ when centered?
    r13=.47,
    r23=.42,
    n=542)
```
Post hoc "power"
```{r posthoc}
MRC(ry1=-.18,
    ry2=-.03,
    ry3=-0.02, 
    r12=.64,
    r13=.47,
    r23=.42,
    n=542)
```

Effect size of 0.01 (which is somewhat ambitious already)

```{r sillence_pwr2ppl}
sillence_pwr2ppl = regintR2(R2Mod = 0.06,
         R2Ch = 0.01,
         mod_pred = 3,
         ch_pred = 1,
         nlow = 500,
         nhigh = 1500,
         by = 25)

sillence_pwr2ppl %>% 
  filter(Power > 0.8) %>% 
  filter(Power == min(Power))
```
This approach predicts that we need n = 750 to get to Power = 0.80 using this analytical approach.

We can plot the power curve as well.

```{r sillence_pwr2ppl_plot}
sillence_pwr2ppl %>% 
  ggplot(aes(n, Power)) + 
  geom_line() + geom_hline(yintercept = 0.8, color = "blue", linetype = "dashed")
```

## InteractionPowerR

### Calculate R2

What correlation between x1x2 and y corresponds with an R^2 change of 0.01?
```{r ipr_an_r2}
ipr_an_r2 = power_interaction_r2(N = 500,
                                                  r.x1.y = -0.18,
                                                  r.x2.y = -0.03,
                                                  r.x1.x2 = 0.64,
                                                  r.x1x2.y = seq(0.1, 0.11, by = 0.001),
                                                  alpha = 0.05,
                                   detailed_results = TRUE) %>% 
mutate(totalr2 = (b1*r.x1.y) + (b2*r.x2.y) + (b3*r.x1x2.y),
       null2 = (b1*r.x1.y) + (b2*r.x2.y),
       r2change = totalr2-null2)

power_interaction_r2(N = 500,
                                                  r.x1.y = -0.18,
                                                  r.x2.y = -0.03,
                                                  r.x1.x2 = 0.64,
                                                  r.x1x2.y = 0.1,
                                                  alpha = 0.05,
                                   detailed_results = TRUE) %>% 
mutate(totalr2 = (b1*r.x1.y) + (b2*r.x2.y) + (b3*r.x1x2.y),
       null2 = (b1*r.x1.y) + (b2*r.x2.y),
       r2change = totalr2-null2)


ipr_an_r2_result = ipr_an_r2 %>% 
  filter(r2change > 0.01) %>% 
  filter(r2change == min(r2change)) %>%
  distinct %>% 
  select(r.x1x2.y, pwr, totalr2, null2, r2change)
  

ipr_an_r2_result

```
```{r regintR2_comparison}
library(pwr2ppl)
regintR2_comparison = regintR2(R2Mod = 0.0547,
         R2Ch = 0.01,
         mod_pred = 3,
         ch_pred = 1,
         nlow = 500,
         nhigh = 500,
         by = 100)
```
```{r MRC}
MRC(ry1=-.18,
    ry2=-.03,
    ry3=0.10,
    r12=.64,
    r13=0,
    r23=0,
    n = 500,
    alpha = 0.05)
```


### Perfect reliability

```{r ipr_an_r1.0, echo = TRUE}
ipr_an_r1.0 = power_interaction_r2(N = seq(500, 1500, by = 0.25),
                                                  r.x1.y = -0.18,
                                                  r.x2.y = -0.03,
                                                  r.x1.x2 = 0.64,
                                                  r.x1x2.y = 0.1,
                                                  alpha = 0.05,
                                   detailed_results = TRUE)
ipr_an_r1.0_0.8 = ipr_an_r1.0 %>% 
  filter(pwr > 0.8) %>% 
  filter(pwr == min(pwr)) %>% 
  distinct

ipr_an_r1.0_0.8

```
```{r ipr_an_r1.0_n500}
ipr_an_r1.0_n500 = power_interaction_r2(N = 500,
                                        r.x1.y = -0.18,
                                        r.x2.y = -0.03,
                                        r.x1.x2 = 0.64,
                                        r.x1x2.y = seq(0.1, 0.2, by = 0.01),
                                        alpha = 0.05)

ipr_an_r1.0_n500 %>% 
  filter(pwr > 0.8) %>% 
  filter(pwr == min(pwr)) %>% 
  distinct
```

```{r plot_ipr_an_r1.0}
ipr_an_r1.0 %>% 
  ggplot(aes(N, pwr)) +
  geom_line() +
  geom_hline(yintercept = 0.8, color = "blue", linetype = "dashed")

```

### Reported reliability
```{r ipr_an}
ipr_an = power_interaction_r2(N = seq(500, 1500, by = 0.25),
                              r.x1.y = -0.18,
                              r.x2.y = -0.03,
                              r.x1.x2 = 0.64,
                              r.x1x2.y = 0.1,
                              rel.y = 0.79,
                              rel.x1 = 0.89,
                              rel.x2 = 0.95,
                              alpha = 0.05)

ipr_an %>% 
  filter(pwr > 0.8) %>% 
  filter(pwr == min(pwr)) %>% 
  distinct

```
When unreliability factored in, much higher N needed even for power of 0.8!
```{r plot_ipr_an}
ipr_an %>% 
  ggplot(aes(N, pwr)) +
  geom_line() +
  geom_hline(yintercept = 0.8, color = "blue", linetype = "dashed")

```
## Save results
```{r Sillence_analytic_results.Rdata}
save(sillence_pwr2ppl, ipr_an_r2, ipr_an_r1.0, ipr_an, file = "Sillence_analytic_results.Rdata")
```

